\thesistitle

### 2019-08-20 sections/experimentalsetup.tex
Experimental setup

\section{Calculating a maintainability score}\label{sec:metricformula}
In this study, we use four metrics to determine maintainability (see Section~\ref{sec:metrics}). For our experiments, we aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring. We base our aggregation on the following assumptions:
\begin{itemize}
  \item All metrics are equal in terms of weight towards system maintenance effort.
  \item Higher values for the metrics imply lower maintainability.
  \item The obtained increase of the metric divided by the average distance from zero over our corpus weights the metric equally against the other metrics.
\end{itemize}
We derived these assumptions partly from Heitlager et al~\cite{heitlager2007practical} and our own expert intuition. The validity of these metrics influences the validity of the conclusions we can draw from our data. Because of that, in our experiments we focus mainly on significant differences in maintainability to draw a conclusion.

By dividing the obtained metric scores by the average distance from zero of all obtained values for a specific metric, we ensure that each metric is weighted equally towards the final maintainability score. We calculate this average distance as follows:
\begin{equation}\label{eq:scoredev}
A = \frac{\sum_{x \in M} abs(x)}{|M|}
\end{equation}
Where \textit{M} is the multiset of all metric increase/decrease values for all refactorings applied to a certain metric over our corpus. \textit{|M|} is the cardinality of this multiset. We then calculate the maintainability for a specific refactoring as follows:
\begin{equation}\label{eq:scoreref}
A_M = \frac{dup}{A_{dup}} + \frac{com}{A_{com}} + \frac{par}{A_{par}} + \frac{vol}{A_{vol}}
\end{equation}
Where \textit{dup} is the decrease in duplication, \textit{com} is the decrease in complexity, \textit{par} is the decrease is method parameters and \textit{vol} is the decrease in system volume after the refactoring is applied. When comparing the maintainability of a set of refactorings we divide the sum of the maintainability score by the amount of clone instances of all refactored clones in the set.

>>>>

\section{Calculating a maintainability score}\label{sec:metricformula}
In this study, we use four metrics to determine maintainability (see Section~\ref{sec:metrics}). For our experiments, we aggregate the deltas obtained for these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring. We base our aggregation on the following assumptions:
\begin{itemize}
  \item All metrics are equal in terms of weight towards system maintenance effort.
  \item Higher values for the metrics imply lower maintainability.
  \item Normalizing each obtained metric delta over all deltas obtained a metric in our dataset results in equally weighted scores.
\end{itemize}
We derived these assumptions partly from Heitlager et al~\cite{heitlager2007practical} and our own expert intuition. The validity of these metrics influences the validity of the conclusions we can draw from our data. Because of that, in our experiments we focus mainly on significant differences in maintainability to draw a conclusion.

We normalize each obtained metric delta using the ``Standard score'', which is as follows:
\begin{equation}\label{eq:scoredev}
N_{metric} = \frac {\delta X-\mu}{\sigma}
\end{equation}
Where $\delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metrics. This method works well for normalization of our data, because as we divide by the standard deviation, outliers do not influence the resulting scores much.

We then calculate the maintainability for a specific refactoring as follows:
\begin{equation}\label{eq:scoreref}
N_{duplication} + N_{complexity} + N_{volume} + N_{parameters}
\end{equation}
